---
title: "R Notebook"
output: html_notebook
---
Machine Learning with Burlington Housing Data

```{r}
rm(list=ls())
library('ggplot2') # visualization
library('scales') # visualization
library('dplyr') # data manipulation
library('mice') # imputation
library('randomForest') # classification algorithm

wholedf <- read.csv("C:/Users/kefor/Desktop/RLearning/City_of_Burlington_Property_Details.csv", header = TRUE)
dim(wholedf)
```
Verify the Structure of the dataframe

```{r}
str(wholedf)
```
Check if there are any null values for any categories.
```{r}
colSums(sapply(wholedf, is.na))
```

```{r}
wholedf <- subset(wholedf, LandUse == "1 Family" | LandUse == "2 Family" | LandUse == "3 Family" | LandUse == "4 Family" | LandUse == "Apartments 5+Units" | LandUse == "Condo")

(wholedf <- wholedf[,c(1,2,4,6,8,9,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,31,32,33,34,35,36,37,38)])

dim(wholedf)
```

```{r}
str(wholedf)
# Show Grade counts by LandUse
table(wholedf$Grade, wholedf$LandUse)
```

```{r}
ggplot(wholedf, aes(CurrentValue, TotalGrossArea, colour = Grade)) + 
  geom_point()
```

```{r}
# Create a family size variable including the passenger themselves
full$Fsize <- full$SibSp + full$Parch

# Create a family variable 
full$Family <- paste(full$Surname, full$Fsize, sep='_')
```

```{r}
plot(wholedf$Grade, wholedf$CurrentV, main="Scatterplot", xlab="X Axiz ", ylab="Y Axis", pch=19)

```


```{r}
ggplot(wholedf, aes(x=log(Sepal.Width+1))) + geom_histogram(col = 'white') + theme_light()
```

```{r}
barplot(wholedf$TotalGrossArea)
```

```{r}
wholedf <- subset(wholedf, c("AccountNumber","ParcelID","StreetNumber","StreetName","Unit","CuO1LastName","CuO1FirstName","LandUse","CurrentAcres","TotalGrossArea","FinishedArea","CurrentValue","CurrentLandValue","CurrentYardItemsValue","CurrentBuildingValue","BuildingType","HeatFuel","HeatType","Grade","YearBlt","SaleDate","SalePrice","NumofRooms","NumofBedrooms","Baths","NumofUnits","ZoningCode","Foundation","Depreciation","PropertyCenterPoint"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
